Glyph-maps for visualizing climate data and models

### 2011-09-19 paper.tex
data example
putting better climate data examples in

@@

@@

**** This is different - I thnk it just confuses the topic of scaling. Because the GAM is not used to rescale the data, you still have to do that using the local or global scling equations above. Moving the discussion to ``What to plot''.

@@

>>>>

% Found data: http://www.esrl.noaa.gov/psd/data/gridded/data.HADCRUT2.html
%     air.mon.anom.nc, var adj, this is 5x5 degree grid, a bit sparse
% Or: http://www.esrl.noaa.gov/psd/data/gridded/data.gisstemp.html
% air.2x2.mon.anom.land.nc 250k smooth data, is on a 2x2 grid

@@

*** These figures need to be placed yet, but are here as a start on better climate data examples:

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\linewidth]{gistemp-raw}%

  \includegraphics[width=1\linewidth]{gistemp-polar-raw}

  \caption{Glyph-maps of gridded raw temperature anomaly data}
  \label{fig:ref-gistemp}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\linewidth]{gistemp-pred}%

  \includegraphics[width=1\linewidth]{gistemp-polar-pred}

  \caption{Glyph-maps of gridded predicted temperature anomaly data}
  \label{fig:ref-gistemp}
\end{figure}

@@

**** This is different - I think it just confuses the topic of scaling. Because the GAM is not used to rescale the data, you still have to do that using the local or global scling equations above. Moving the discussion to ``What to plot''.

@@

\section*{Acknowledgements}

GISTEMP data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado,
USA, from their Web site at \url{http://www.esrl.noaa.gov/psd/}.
